---
name: Jim Murphy
date: "`r format(Sys.time(), '%B, %Y')`"
qualifications: MPhys (Hons)
position: Data Engineer
address: London
#profilepic: "./img/me.jpg"
www: jmrph.org
github: j-mrph
email: jmrph@protonmail.com
headcolor: 414141
output: 
  vitae::awesomecv:
    keep_tex: true
---

```{r setup, include=FALSE}
library(dplyr)
library(vitae)
knitr::opts_chunk$set(echo = FALSE)
```

# About
Accomplished data engineer with a track record of delivering robust, scalable cloud data pipelines and analytics. Specialises in production-grade workflow automation and enabling business insights for large organisations via modern cloud platforms.

# Skills
**Languages/Tools:** Python (pyspark), SQL (Snowflake + SQL Server), dbt, Airflow (self-hosted + Astronomer), Azure (Databricks, DataFactory), AWS (S3, EC2, Lambda), Terraform, Kafka

**Expertise:** Data pipeline architecture, real-time data ingestion, cloud infrastructure, CI/CD


# Experience

```{r work exp}
tribble(
  ~role, ~company, ~loc, ~dates, ~details,

  # Sainsbury's Tech
  "Data Engineer", "Sainsbury's Tech", "London, U.K.", "Oct. 2022 - Present", "Prototyped, built and maintained the data backend of an external facing data platform for Sainsbury's suppliers to securely access their data. Worth upwards of £3 million in annual revenue.",
  "Data Engineer", "Sainsbury's Tech", "London, U.K.", "Oct. 2022 - Present", "Led on infosec upgrades, test coverage and migration from legacy Jenkins infrastructure using Terraform, AWS and GitHub Actions.",
  "Data Engineer", "Sainsbury's Tech", "London, U.K.", "Oct. 2022 - Present", "Built and deployed real-time supply chain data pipelines using Kafka, Airflow, and Snowflake models in dbt. Enabled robust stream processing for critical business operations.",
  


  # Analyst


  "Data Engineer / Data Analytics Dev", "National Audit Office", "London, U.K.", "Sep. 2019 - Present", "Developed reproducible cloud based pipelines in Pyspark conforming incoming varied audit data totalling billions of records into a standardised database using combination of DataFactory, Databricks and SQL.",
  "Data Engineer / Data Analytics Dev", "National Audit Office", "London, U.K.", "Sep. 2019 - Present", "Built and deployed live service wide audit automation analytic with 300+ users. Integrating CI/CD best practices with built in unit testing in Azure release pipeline.",
  "Data Engineer / Data Analytics Dev", "National Audit Office", "London, U.K.", "Sep. 2019 - Present", "Introduced robust app user authentication using OAuth and Azure Active Directory in service wide R Shiny apps for large scale user tracking and security measures regarding data access.",






  # Secondment

  "Data Analytics Developer (secondment)", "Government Actuary's Department", "Remote", "Spring 2021", "Developed actuarial tools in Python Dash to increase speed and quality of salary modelling.",
  "Data Analytics Developer (secondment)", "Government Actuary's Department", "Remote", "Spring 2021", "Introduced a small development team to effective version control using git to better manage deployments and collaboration on shared code.",




  # data science internship
  "Data Science Intern", "National Audit Office", "London, U.K.", "Aug. 2018 - Sep. 2019", "Developed an automated sprint report system using DevOps API, for review by my team to assess bottlenecks and progress against key objectives.",
  "Data Science Intern", "National Audit Office", "London, U.K.", "Aug. 2018 - Sep. 2019", "Built application making use of web scraping, text analysis and visualisation to bulk confirm audit fees of NAO clients garnering interest from international audit institutions.",
) %>%
  detailed_entries(role, dates, company, loc, details)
```

# Education
```{r education}
tribble(
  ~degree, ~uni, ~loc, ~dates, ~details,
  "Master of Physics (First Class)", "University of Liverpool", "Liverpool, U.K.", "Sep. 2013 - Jul. 2017", "Making use of strong numerical and analytical skills, the ability to find underlying patterns in seemingly chaotic data allowed me to excel during my studies.",
  "Master of Physics (First Class)", "University of Liverpool", "Liverpool, U.K.", "Sep. 2013 - Jul. 2017", "Harnessed my ability to work effectively as part of a team or on an independent basis to deliver accurate results regardless of pressure or workload.",
  "Master of Physics (First Class)", "University of Liverpool", "Liverpool, U.K.", "Sep. 2013 - Jul. 2017", "In weekly report writing and lab work tasks I have enhanced my written and verbal communication skills allowing me to produce concise documents within strict time constraints."
) %>%
  detailed_entries(degree, dates, uni, loc, details)
```